---
output:
  html_document:
    css: "www/custom.css"
runtime: shiny_prerendered
author: Environmental Cheminformatics Group, LCSB, University of Luxembourg
title: "`r paste('Shinyscreen', packageVersion('shinyscreen'))`"
---

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(system.file(package="shinyscreen","www/shinyscreen2.png")), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:5px;')
```


```{r, context='setup', include='false'}
library(data.table)
library(shinyscreen)
library(ggplot2)
### library(shinydashboard)

init <- readRDS("init.rds")
def_state <- new_state()
def_datafiles <- shinyscreen:::dtable(file=character(0),
                                      tag=character(0))
def_datatab <- shinyscreen:::dtable("tag"=factor(),
                                    "adduct"=factor(levels=shinyscreen:::DISP_ADDUCTS),
                                    "set"=factor())

def_summ_subset <- shinyscreen:::dtable("QA Column"=shinyscreen:::QA_FLAGS,
                                        "Select"=factor("ignore",levels=shinyscreen:::SUBSET_VALS))
### RMassBank masks shiny::validate. Unmask it.
validate <- shiny::validate
### def_state$input$tab$tags <- def_datatab
rv_state <- list2rev(def_state)

### Reactive values to support some of the UI elements.
### rv_ui <- reactiveValues(datatab=def_tags)

### Update with data-files.
rv_dfile <- reactiveVal(def_datafiles)

### Data-file table when loading.
rv_datatab <- reactiveVal(def_datatab)

### Re-definitions.
PLOT_FEATURES <- shinyscreen:::PLOT_FEATURES

### Plotting parameters.

### Transient rt range.
rv_rtrange <- reactiveValues(min=def_state$conf$rt_min,
                             max=def_state$conf$rt_max)

### Transient mz range.
rv_mzrange <- reactiveValues(min=NA,
                             max=NA)

projects <- list.dirs(path=init$envopts$projects, full.names = F, recursive = F)
inputdirs <- list.dirs(path=init$envopts$top_data_dir, full.names = F, recursive = F)

```
<style type="text/css">
.main-container {
  max-width: 100%;
  margin-left: auto;
  margin-right: auto;
}
</style>

# {.tabset .tabset-pills}

## Project {.tabset}

```{r, child='app_project.Rmd'}
```


## Configure, Extract, Prescreen {.tabset}

<div class = "flex-cols"> <!-- confstatus-panes -->
<!-- confstatus-panes-left -->
<div>					
```{r, child='app_config_and_status.Rmd'}
```
</div> <!-- confstatus-panes-left -->
<div>  <!-- confstatus-panes-right -->

#### Control

<div style="display: flex;flex-flow: row wrap;">
```{r, echo=FALSE}
actionButton(inputId = "extract_b",
             label = "Extract")
```

```{r, echo=FALSE}
actionButton(inputId = "presc_b",
             label = "Prescreen")
```
</div>

#### Overview

- Has the data been extracted? `r htmlOutput("is_extracted_stat", inline=T)`
- Has the data been auto-quality checked? `r htmlOutput("is_qa_stat", inline=T)`

##### Extraction

- MS1 coarse: `r htmlOutput("ms1_coarse_stat", inline=T)`
- MS1 fine: `r htmlOutput("ms1_fine_stat", inline=T)`
- MS1 eic: `r htmlOutput("ms1_eic_stat", inline=T)`
- Retention time window: `r htmlOutput("rt_stat", inline=T)`

##### Prescreening

- Intensity Threshold (MS1): `r htmlOutput("ms1_int_thresh_stat", inline=T)`
- Intensity Threshold (MS2): `r htmlOutput("ms2_int_thresh_stat", inline=T)`
- Retention time shift: `r htmlOutput("ret_time_shift_tol_stat", inline=T)`
- Signal-to-noise ratio: `r htmlOutput("s2n_stat", inline=T)`



</div> <!-- confstatus-panes-right -->
</div> <!-- confstatus-panes -->


<!-- TODO: This should be readded at some point. -->
<!-- ```{r, child='app_compound_lists_and_sets.Rmd'} -->
<!-- ``` -->


## Results Explorer

<details>
<summary>Learn more about compound index</summary>

Compound index is used to select entries from the input compound/mass
lists. What exactly is going to be shown depends on what was chosen
using the *Group* control. The *Group* control allows user to choose
which features of data should be used to group entries together. For
example, if there are multiple input data files, then grouping by
*tag* will result in a single compound index entry for all the ions of
the same adduct type, the same ID across the different data files. If
a user additionally selects *adduct*, then a single entry represents
masses belonging to the same compound ID, even if they are of
differing adduct types.

**IMPORTANTLY**, the metadata such as *mz*, or retention time are
**averages** over the group of of results belonging to the same
compound index entry. If the exact mass of a singe entry is needed,
consult the summary table. Alternatively, remove grouping and you 
shall get non-averaged values.

The second group of controls influence the precedence of parent
features when determining the order of items in the compound index.

There two derived quantities, *qlt_ms1* and *qlt_ms2*. The only
purpose they serve is to help sorting the data. The highest score in
any of the two categories is ten. If an index entry scores ten, this
means that at least one in the collection of results represented by
the index has passed all the quality checks.

When an entry of the index is selected, the plots of its EICs and MS2
spectra (if any) are shown in the plotting section. Each result in the
index entry collection is represented by a single line. 

For example, let there be six data files, the three of them scanned
for [M+H]+ and the other three for [M-H]- ions. If the index is
grouped by only by *tag*, there exists a compound with the ID 42, then
the compound index is going to contain two entries for compound 42,
one labelled by [M+H]+ in the adduct column and another labelled with
[M-H]-. If one of those entries is selected, a single EIC, or mz plot
is going to contain three lines, each representing a single *tag*. If,
additionally, the results are grouped by *adduct*, the index is going
to contain only a single entry for the ID 42. The plot, in this case,
contains six lines (for each existing combination of tag and adduct).

</details>
<div class='flex-layers'> 
```{r, child='app_results_explorer_cindex.Rmd'}
```
<details>
<summary>Operations over compound index.</summary>

- **Report** is currently a collection of all plots of items in the compound index.
- **Summary table** comprises of all the metadata related to parent ions and the selected MS2 spectra (if present).
- **Table of MS2 spectra** contains information on all the MS2 spectra and their parents.
- **MetFrag summary table** contains a summary of the MetFrag results for all compound index entries.

</details>
```{r, child='app_results_explorer_cindex_controls.Rmd'}
```
</div>
<div class="flex-panes">
<!-- index-viewer-panes -->
<div style="flex-basis: 80%;">
```{r, child='app_results_explorer_viewer.Rmd'}
```
</div>
<div>
```{r, child='app_results_explorer_viewer_ctrls.Rmd'}
```
</div>
</div> <!-- index-viewer-panes -->

```{r, child='app_measure_props.Rmd'}
```

```{r, child='app_results_explorer_metfrag.Rmd'}
```

<!-- ENGINE -->

```{r, echo = F, context = 'setup'}
shinyscreen_server <- shinyscreen:::mk_shinyscreen_server(projects=projects,
                                                          init=init)
```

```{r, echo = F, context = 'server'}
shinyscreen_server(input=input,output=output,session=session)
```

