<details><summary>Extract spectra from data files.</summary>

Spectral extraction is controled by the parameters under the
_Extraction_ tab, while the quality check parameters are located under
the _Prescreening_ tab.

After Shinyscreen is configured, the compound and setid lists loaded,
it is possible to proceed with extracting the data. The extraction
process can start after pressing `Extract`. Depending on the size of
the commpound list and the properties of the data files this may take
a while.

Once the data is extracted, quality checking can be carried out using
the `Prescreen` button.

The parameters affecting current extraction are displayed in the
*Overview* section. 

</details>

### Extraction

#### Spectra extraction based settings

<details><summary>MS1 coarse error</summary>

Extract all entries matching the target mass within this error in the
precursor table.
</details>
```{r, echo=F}
vu <- get_val_unit(def_state$conf$tolerance[["ms1 coarse"]])
shinyscreen::mz_input(input_mz = "ms1_coarse",
                       input_unit = "ms1_coarse_unit",
                       def_mz = vu[['val']],
                       def_unit = vu[['unit']])
```

<details><summary>MS1 fine error</summary>

The precursor table masses can be of lower accuracy. Once there is a
match within the coarse error, it can be further checked versus the
fine error bounds directly in the mass spectrum.

</details>
```{r, echo=F}
vu <- get_val_unit(def_state$conf$tolerance[["ms1 fine"]])
shinyscreen::mz_input(input_mz = "ms1_fine",
                      input_unit = "ms1_fine_unit",
                      def_mz = vu[['val']],
                      def_unit = vu[['unit']])
```

<details><summary>MS1 EIC window</summary>

The mz interval over which the intensities are aggregated to generate
a chromatogram.

</details>
```{r, echo=F}
vu <- get_val_unit(def_state$conf$tolerance[["eic"]])
shinyscreen::mz_input(input_mz = "ms1_eic",
                      input_unit = "ms1_eic_unit",
                      def_mz = vu[['val']],
                      def_unit = vu[['unit']])
```

<details><summary>Retention time window</summary>

If the expected retention time has been specified for the compound,
then search for the MS1 signature inside the window defined by this
range.

</details>
```{r, echo=F}
vu <- get_val_unit(def_state$conf$tolerance[["rt"]])
shinyscreen::rt_input(input_rt = "ms1_rt_win",
                      input_unit = "ms1_rt_win_unit",
                      def_rt = vu[['val']],
                      def_unit = vu[['unit']])
```

<details><summary>Fill missing precursors</summary>

* **fill** : Try to guess precursors of MS2 entries. This is done by
picking MS1 which chronologically preceeds a given MS2 entry.
* **omit** : Ignore MS2 with missing precursors.
* **do_nothing** : Default. Use MS1--MS2 metadata recorded in the file
to associate MS1 and MS2 entries. Usually works.  
</details>
```{r, echo=F}
radioButtons("missingprec",
             label = "Missing precursors",
             choices = c("do_nothing","fill","omit"),
             selected = "do_nothing")

```

### Prescreening

<details><summary>MS1 intensity threshold</summary>

Ignore MS1 signal below the threshold.

</details>
```{r, echo=F}

numericInput(inputId = "ms1_int_thresh",
             label = NULL,
             value = def_state$conf$prescreen$ms1_int_thresh)
```

<details><summary>MS2 intensity threshold</summary>

Ignore MS2 signal below the threshold.

</details>
```{r, echo=F}

numericInput(inputId = "ms2_int_thresh",
             label = NULL,
             value = def_state$conf$prescreen$ms2_int_thresh)
```


MS1 signal-to-noise ratio.

```{r, echo=F}

numericInput(inputId = "s2n",
             label = NULL,
             value = def_state$conf$prescreen$s2n)
```


<details><summary>MS1/MS2 retention delay.</summary>

Look for associated MS2 spectrum within this window around the MS1
peak.

</details>
```{r, echo=F}
vu <- get_val_unit(def_state$conf$prescreen[["ret_time_shift_tol"]])
shinyscreen::rt_input(input_rt = "ret_time_shift_tol",
                      input_unit = "ret_time_shift_tol_unit",
                      def_rt = vu[['val']],
                      def_unit = vu[['unit']])
```

### MetFrag (`r htmlOutput("cando_metfrag", inline=T)`)

<!-- If `java` and `MetFragCL` are available, Shinyscreen can run -->
<!-- `MetFragCL`. The configuration is a subset of what a MetFrag config -->
<!-- file looks like. -->


<div class="flex-cols"> <!-- metfrag-conf-box-1 -->
<div> <!-- metfrag-conf-tolerance -->

#### Tolerance and Tree Depth Controls

```{r, echo=F}
inject_inputs(INPUTS_METFRAG,c("mf_fragment_peak_match_absolute_mass_deviation",
                               "mf_fragment_peak_match_relative_mass_deviation",
                               "mf_database_search_relative_mass_deviation",
                               "mf_maximum_tree_depth"))
```
</div> <!-- metfrag-conf-tolerance -->

<div> <!-- metfrag-conf-processing -->

#### Processing

```{r, echo=F}
inject_inputs(INPUTS_METFRAG,c("mf_pre_processing_candidate_filter",
                               "mf_post_processing_candidate_filter",
                               "mf_metfrag_candidate_writer"))
```
</div> <!-- metfrag-conf-processing -->

<div> 

<!-- metfrag-conf-execution -->
#### Execution

<details><summary>More about execution controls</summary>

The `Number of MetFrag Processses` field will show the maximum amount
of logical threads available on the platform which executes
MetFrag. Consider that, if you use all of them, this might cause an
overload of the system's resources.

</details>

```{r, echo=F}
## This is treated differently than other MF inputs, because the value
## is not known prior to starting a R session. There should be a
## mechanism for this. TODO FIXME.

numericInput(inputId="mf_proc",
             label="Number of MetFrag processes",
             value=init$envopts$metfrag$max_proc)
```

</div> <!-- metfrag-conf-execution -->

</div> <!-- metfrag-conf-box-1 -->

<div class="flex-cols"> <!-- metfrag-conf-box-2 -->
<div> <!-- metfrag-conf-databases -->

#### Databases

<details><summary>More about databases</summary>

MetFrag offers a possibility to query different chemical
databases. Some, such as `PubChem` are remote and some, such as
`PubChemLite` are files that can be downloaded and used locally. At
the moment, Shinyscreen has only been well tested with `LocalCSV`
databases --- those which come in a CSV format. The Shinyscreen
development team is keen to hear experiences of experimentation with
other sources and. Let us know what works, or does not work and
whether having other sources available is important for your
endeavours.

As for the `LocalCSV` types of databases, on an abstract level they
can be viewed as collections of metadata about various
compounds. There will be *identifier* fields which are unique to a
compound. As an example, those could be `Identifier`, or
`CompoundName` columns in a PubChemLite database. Additionally, there
will be lots of other fields, some of which can be used as *scoring
terms*. For example, annotation, patent and PubMed count columns in a
PubChemLite database can be used by MetFrag to aid sensible ranking of
candidates.

Local databases should all reside in a directory that was specified
during Shinyscreen initialisation (look up the documentation of the
`Shinyscreen::init` function).

User selects the local databases from 
`r inputs_html_out(INPUTS_METFRAG,"mf_local_database")` 
control. Once a database is selected, it is required 
to declare which columns are the identifiers 
and this is done using 
`r inputs_html_out(INPUTS_METFRAG,"mf_local_db_col_ident")`.

The summary of MetFrag results which is created by Shinyscreen
contains top candidates. But, in addition to those, it will show a
collection of other candidates, those that did not rank that high. The
identifier filed which will be used for those can be chosen from
`r inputs_html_out(INPUTS_METFRAG,"mf_local_db_col_coll")`.
In case of PubChemLite, it is probably best to select `Identifier` column here.



</details>

```{r, echo=F}
inject_inputs(INPUTS_METFRAG,c("mf_database_type",
                               "mf_local_database",
                               "mf_local_db_col_ident",
                               "mf_local_db_col_coll"))
```

</div> <!-- metfrag-conf-databases -->

<div> <!-- metfrag-conf-mf-scores -->

#### MetFrag Scores

<details><summary>About MetFrag scoring terms</summary>
Here, it is possible to select MetFrag scoring types available for any
kind of database.
</details>

```{r, echo = F}
inject_inputs(INPUTS_METFRAG,"mf_scores_intrinsic")
DT::DTOutput("mf_local_ident")
```

</div> <!-- metfrag-conf-mf-scores -->
<div>  <!-- merfrag-conf-local-db-scores -->

#### Local Database Scoring Terms

<details><summary>About local DB scoring terms</summary>
Select local database columns that make sense as scoring terms.
</details>


```{r, echo = F}
inject_inputs(INPUTS_METFRAG,"mf_local_db_col_scores")
DT::DTOutput("mf_local_db_scores")
```

</div> <!-- merfrag-conf-local-db-scores -->
</div> <!-- metfrag-conf-box-2 -->

### Report

Parameters to control the report output not yet available.

<!-- <details><summary>Create a report</summary> -->

<!-- Shinyscreen can produce a report containing graps of EICs and spectra -->
<!-- for some or all compounds. The controls below define what enters the -->
<!-- report. Please keep in mind that producing a PDF output with thousands -->
<!-- of compounds will take huge amount of time, so if you are prescreening -->
<!-- a lot of compounds, consider restricting limiting the output to, for -->
<!-- example, those entries that have passed the quality checks. -->

<!-- </details> -->

<!-- ```{r, echo=F} -->
<!-- shiny::textInput(inputId = "rep_aut", label = "Report author", value = def_state$conf$report$author) -->
<!-- shiny::textInput(inputId = "rep_tit", label = "Report title", value = def_state$conf$report$title) -->
<!-- ``` -->


