### MetFrag Summary Viewer

<details>
<summary>About the MetFrag summary viewer</summary>

If MetFrag is available (this can be enabled usint the
`shinyscreen::init` function), then, clicking on the button will
generate a MetFrag summary for the selected compound index entry.

It is possible to limit the spectra for MetFrag analysis by defining
the retention time interval using the controls under `MS2 Retention
Time Interval` section.

</details>


#### MS2 Retention Time Interval

<div class="flex-ctrl-row"> 
<!-- RT div -->
```{r, echo=F}
numericInput(inputId = "mf_entry_rt_min",
             label="Start",
             value=NA_real_,
             width="10%")
```
```{r, echo=F}
numericInput(inputId = "mf_entry_rt_max",
             label="End",
             value=NA_real_,
             width="10%")

```
</div> <!-- RT div -->


```{r, echo=F}
actionButton(inputId = "gen_mf_single_entry_summ_b",
             label= "Process compound")
```
MS2 Retention Time Interval


```{r, echo=F}
actionButton(inputId = "save_mf_single_entry_summ_b",
             label= "Save table")
htmlOutput("entry_mf_summ_fname")
DT::DTOutput("entry_mf_summ")
```
