<details>
<summary>Projects, input directories and compound lists</summary>

When you start the program with `app` function, you define two
superdirectories: `projects` and `top_data_dir`. Directory `projects` contains
all the existing projects and any new projects defined during the
current session will be saved here. Data inside a project directory
consists of intermediate files, saved states and workflow outputs.

To create a new project, type in the name and press the `Create`
button. To load a project, select the project and press `Load`.

There is also a possibility to save the current project state. Just
use the `Save project` button. This action will record all your
settings and selected inputs.

Each `Shinyscreen` project needs input data: mass spectrometry files
(in mzML format), compound and set lists. These should all be present
before starting `Shinyscreen` in one of the directories under
`projects`.



</details>

### Project management

#### Load or initialise a project

<details>
<summary>Load, or initialise a project</summary>

All projects are shown in the `Avaliable projects`
list. Load the project by pressing `Select project` button. 

If the project is new, it has to contain the compound list(s) and the
set list.

</details>

```{r, echo=F}
selectInput('proj_list',
            label = "Select project",
            choices = projects)
actionButton(inputId = "load_proj_b",
             label= "Load/Initialise")
textOutput("curr_proj")

```


#### Save project
```{r, echo=F}
actionButton(inputId = "save_proj_b",
             label= "Save project")
```

#### Download project

<details> 
<summary>Download results</summary>

Button `Download project` only makes sense to be used if Shinyscreen is
served over network. If this is the case, clicking this button will
download plots and csvs generated in the project directory.
</details>

```{r, echo=F}
downloadButtonRmd <- function (outputId, label = "Download", class = NULL, ...)  {
     tags$a(id = outputId, class = paste("btn btn-default shiny-download-link", 
        class), href = "", target = "_blank", download = NA, 
        icon("download"), label, ...)
 }

downloadButtonRmd("dwn_proj_b",
                  "Download project directory")
```


#### Select data directory
<details>
<summary>More on data directories</summary>

Data directory is a subdirectory of the `top_data_dir` directory which is
one of the arguments to `app` function used to start Shinyscreen
GUI. It contains the `mzML` data files.

Select one of the data directories from the list by clicking the
`Select` button.

</details>

```{r, echo=F}
selectInput('top_data_dir_list',
            label = "Input directories",
            choices = inputdirs)
actionButton(inputId = "sel_data_dir_b",
             label= "Select")
textOutput("curr_data_dir")
```

### Compound list inputs

#### Select compound lists

<details><summary>About compound lists</summary>
A compound list is composed of entries describing compounds. This
description is used to search for its spectrum in the data file. The
list is a table in the ***CSV*** format and contains these columns,

* ***ID*** : required column, must be filled; this is a user-defined
  ID, uniquely associated with a compound
  
* ***Name*** : this column can be left blank; if not, it should contain the
  names of the compounds
  
* ***SMILES*** : a _SMILES_ string, describing the structure of the
  compound; this entry can be left empty only if one of either
  ***Formula***, or ***mz*** entries are not
  
* ***Formula*** : a chemical formula of a compound; this field can be
  empty only if one of either ***SMILES***, or ***mz*** entries are
  not
  
* ***mz*** : mass of the ionised compound; this field can be left
  empty only if one of either ***SMILES***, or ***Formula*** is not
  
* ***CAS*** : the CAS number of the compound; it can be left empty

* ***RT*** : retention time of the MS1 peak in minutes, if known; can
  be left empty.
  
Only ***ID*** and one of ***SMILES***, ***Formula*** or ***mz*** must
be filled. When structure, or a formula of a compound is known, it is
also possible to look for various adducts in the sample. Of course,
scanning for completely unknown compounds is also supported by the
***mz*** column. In this case, ***mz*** is the mass of the ion.

It is strongly recommended to quote SMILES, names and formulas in the
CSV file used with Shinyscreen.

Select one, or more compound lists by clicking `Select` button.
</details>

<div style= "display: flex; vertical-align:top; padding-right: 1.0em"> <!-- comp-list-box -->

<div> <!-- comp-list-sel -->
```{r, echo=FALSE}
selectInput('comp_list',
            label = "Select compound lists",
            multiple = T,
            choices = "")
actionButton(inputId = "comp_list_b",
             label= "Select")

```
</div> <!-- comp-list-sel -->

<div> <!-- comp-list-disp -->

**Selected compound lists**

```{r, echo=FALSE}
htmlOutput('comp_list_report')
```

</div> <!-- comp-list-disp -->

</div> <!-- comp-list-box -->

### Data files
<details><summary>Load data files</summary>

Shinyscreen currently supports only the **mzML** file format. After
loading the files, select the files, then associate them with
appropriate sets and adducts .

</details>
```{r, echo=FALSE}

selectInput('dfile_list',
            label = "Select datafiles",
            multiple = T,
            choices = "")
actionButton(inputId = "datafiles_b",
             label= "Load data files.", width="10%")

```

<div class="flex-ctrl-row" style="align-items:start; column-gap: 1.5rem;">
<!-- datafiles-main-div -->
<div>
<!-- datafiles/tags -->
<details><summary>Assign tags to data files.</summary> 

Each tag designates an unique file. Use the table below to assign
tags.

</details>

```{r, echo=FALSE}
DT::DTOutput("datafiles")## DT::DTOutput("datafiles",width="25%")
actionButton("rem_dfiles_b",label="Remove selected entries")
```
</div> <!-- datafiles/tags -->
<div>
<!-- tag/adduct/set associations -->
<details><summary>Associate tags with adducts and sets.</summary> 

Select file/tag entries you want to associate tags with and then
select those you want from the select control.

Repeat the same for sets.

</details>
```{r, echo=F}
selectInput(inputId="tag_sets_list",
            label="Select set",
            ## multiple=T, #TODO
            choices=NULL,
            selected=NULL)
selectInput(inputId="tag_adducts_list",
            label="Select adducts",
            choices=shinyscreen:::DISP_ADDUCTS,
            multiple=T,
            selected=NULL)
actionButton(inputId="fill_datatab_b",
             label="Fill table")
```

<!-- tag/adduct/set associations -->
</div>
<div>
<!-- datafiles/adducts/tags -->
<details>

<summary>This is the data files table.</summary>

Establishes relationships between tags, sets and adducts.

</details>
```{r, echo=F}
DT::DTOutput("datatab")
actionButton("rem_dtab_b",label="Reset table")
```
</div><!-- datafiles/adducts/tags -->

<!-- datafiles-main-div -->
</div>
